ms_5

### 2020-04-26 ms_5.Rmd
still getting col spec errors

anim_save("plot_deathsbycommondiseases.gif", plot_deathsbycommondiseases)

@@

anim_save("prop_deathsbycommondiseases.gif", prop_deathsbycommondiseases)

@@

death_by_year_and_state <- read_csv("Drug Overdose Deaths by Year and State.csv")

@@

anim_save("plot_mavsus_death.gif", plot_mavsus_death)

>>>>

@@

@@

death_by_year_and_state <- read_csv("Drug Overdose Deaths by Year and State.csv", 
                                    col_types = "lcdccddddddddic")

@@
